Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-09-18 submission/manuscript.Rmd
affiliations and formatting

```
Katherine M. Bonefas, Ilakkiya Venkatachalam, and Shigeki Iwase.

@@

>>>>

```
Katherine M. Bonefas^1,2^, Ilakkiya Venkatachalam^2,3^, and Shigeki Iwase^2^.

1. Neuroscience Graduate Program, University of Michigan Medical School, Ann Arbor, MI, 48109, USA.
2. Department of Human Genetics, Michigan Medicine, University of Michigan Medical School, Ann Arbor, MI, 48109, USA.
3. Genetics and Genomics Graduate Program, University of Michigan, Ann Arbor, MI, 48109, USA.

\newpage

@@

\newpage
